Fractional anisotropy as a tracer of cosmic voids

### 2014-09-13 cosmic_voids.tex
Changing label of plots for FA-WT

In next section we shall describe an alternative approximation to select 
the threshold value $\lambda_{th}$, and as will be shown, one of its main 
advantages is the similar volume filling fraction (VFF) of each 
environment as compared between both web schemes. Using this result, we 
propose here a heuristic classification of the Cosmic Web based on 
three density thresholds assigned to each boundary (i.e. void-sheet, 
sheet-filament and filament-knot)\footnote{The progressive sequence 
void-sheet-filament-knot along any path in the Cosmic Web should be always
satisfied as each used field is smoothed. For instance, it should not be 
possible to find a knot-type cell abutting another sheet or void-type 
cell.} such that the corresponding VFF values are similar to the values 
obtained for the T-web and the V-web, specifically they are defined 
to be the arithmetic mean of both schemes.

>>>>

In next section we shall describe an alternative approximation to select 
the threshold value $\lambda_{th}$, and as will be shown, one of its main 
advantages is the similar volume filling fraction (VFF) of each 
environment as compared between both web schemes. Using this result, we 
propose here a heuristic classification of the Cosmic Web based on 
three density thresholds assigned to each boundary (i.e. void-sheet, 
sheet-filament and filament-knot)\footnote{The progressive sequence 
void-sheet-filament-knot along any path in the Cosmic Web should be always
satisfied as each used field is smoothed.} such that the corresponding VFF 
values are similar to the values obtained for the T-web and the V-web, 
specifically they are defined to be the arithmetic mean of both schemes.
